\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-02-20 src/010chap1.tex
- incorporated new changes to Characterization algorithm. no more exit    statements in algo 1 and 2. however it is not identitcal to n's    version. kept some of the old lemmas because it seems to elucidate    (to me) the thesis. - partial editing done of general tree section (prime matrix theory)    -- TBD - not sure about status of special tree = path section -- TBD
- changed notation for induced path labeling
- changed filter 1 and 2 names.
- poset definition

\begin{definition}
  \label{def:poset}    
%   Let $A$ be a set and $R$ be a binary relation $R \subseteq A \times
%   A$.

%   \textbf{poset}
  Let $X$ be a partially ordered set with $\preccurlyeq$ being the
  partial order on $X$.

@@

We also have an algorithm for solving {\CFTPL} with no restrictions on
the target tree or set size which runs in exponential time.  This
algorithm finds a path labeling from $T$ by decomposing the problem
into subproblems of finding path labeling of subsets of $\cF$ from
subtrees of $T$. Given the fact that binary matrices naturally
represent a set system (see Section~\ref{sec:motive}) and that the
{\em overlap} relation between the sets involved is an obvious
equivalence relation, $\cF$ quite naturally partitions into
equivalence classes known as {\em overlap components}. In the context
of COP, overlap components were used in \cite{wlh02} and
\cite{kklv10}. Moreover, \cite{nsnrs09} discovered that these
equivalence classes form a total order. We extend this to TPL and find
that when $\cF$ is a path hypergraph\footnote{If there exists an FTPL
  for a hypergraph $\cF$, it is called a path hypergraph.}, the
classes can be partially ordered as an in-tree in polynomial
time. Once $\cF$ is ``broken'' into overlap components, one must
identify the subtree of $T$ that it needs to map to and this is the
hard part which is currently open to be solved in polynomial time.

>>>>

\def\posetr{\le}

\begin{definition}[Poset]
  \label{def:posetdef}    
  Let $\posetr$ be a binary relation on a finite set $X$. $\posetr$ is a \textbf{
    partial order} and $\left< X,\posetr \right>$  is a \textbf{ poset}
  if the following hold true for any $a, b, c \in X$.
 \parindent  \defindent 
%  \hangindent \defindent
  \begin{enumerate}
  \item $a \posetr a$ (reflexivity)
  \item If $a \posetr b$ and $b \posetr a$ then $a = b$ (antisymmetry)
  \item If $a \posetr b$ and $b \posetr c$ then $a \posetr c$
    (transitivity)
  \end{enumerate}

  An element $b$ \textbf{covers} $a$ provided that there exists no
  third element $x \in X$ \stt $a \posetr x \posetr b$.  A directed
  (or undirected, but with direction implied by horizontal positioning
  of nodes) graph that represents $\posetr$ in terms of its covering
  relation is called the \textbf{Hasse diagram} of the poset.
\end{definition}

\begin{definition}
  \label{def:poset}    
  Let $X$ be a partially ordered set with $\preccurlyeq$ being the
  partial order on $X$.

@@

We also have an algorithm for solving {\CFTPL} with no restrictions on
the target tree or set size which runs in exponential time.  This
algorithm finds a path labeling from $T$ by decomposing the problem
into subproblems of finding path labeling of subsets of $\cF$ from
subtrees of $T$. Given the fact that binary matrices naturally
represent a set system (see Section~\ref{sec:motive}) and that the
{\em overlap} relation between the sets involved is an obvious
equivalence relation, $\cF$ quite naturally partitions into
equivalence classes known as {\em overlap components}. In the context
of COP, overlap components were used in \cite{wlh02} and
\cite{kklv10}. Moreover, \cite{nsnrs09} discovered that these
equivalence classes form a total order in the case of \COP. We extend this to TPL and find
that when $\cF$ is a path hypergraph\footnote{If there exists an FTPL
  for a hypergraph $\cF$, it is called a path hypergraph.}, the
classes can be partially ordered as an in-tree in polynomial
time. Once $\cF$ is ``broken'' into overlap components, one must
identify the subtree of $T$ that it needs to map to and this is the
hard part which is currently open to be solved in polynomial time.
